Replication Survey

### 2024-02-01 docs/manuscript/manuscript.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Replications confront existing explanations with new evidence by retesting prior claims using new data, while controlling for procedural differences by conducting similar analyses.
Replications can be designed to serve different epistemic functions and to test several forms of validity.
Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories it is based on \citep{earp2015, nichols2021}. 
When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.

@@

The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}. 
Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
With these intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility rather than replicability. 
In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Replication and the Evaluation of Prior Claims}
Replications structure the iterative development of theory by confronting claims with new evidence.
Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings. 
Until tested, whether a claim is expected to hold under new conditions is either a product of the theory used to structure the original investigation, or a speculative assumption of generalizability.
Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.  
By altering different aspects of a study across a series of replications, researchers can collectively and progressively test claims across a widening set of conditions and use that information to revise theory.

The type of check a replication provides depends on which aspects of a study are changed and in what combination. 
Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}. 
Replication studies are often classified either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.

Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, the replication is designed to assess conclusion validity.
As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation. 
Alternatively, a researcher can use a replication to test construct validity, if they change how a key construct is measured and also hold all other aspects of a study constant. 
Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made. 
Finally, when the materials and procedures (e.g., data collection device, analyses) used in a replication differ from an initial study, the replication assesses the whether these factors affected the original results testing the internal validity of the prior work.

In conceptual replications changes are made to the population or location being studied to test external validity and whether the claims made in a study generalize to new populations and contexts. 
In geographic research, a conceptual replication could for example involve changing the location of a study from one city to another, or one ecosystem to another. 
Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after a migration event is through to have changed the population of that area. 
Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
For example, it is not necessarily the case that observing evidence in a one location that contradicts a claim made in study of another location would cause a researcher to reduce their confidence in that initial claim.

As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015}.
When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
Without these statements, it remains possible that the predictions of the theory will generalize across a large set of contexts. 
In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
In this situation, conceptual replications act as empirical tests of the generalizability of a theory to new contexts. 
Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and /or when the theory is expected to provide meaningful predictions.
As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clear.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{The Replicability of Geographic Research}
Geographers have arguably never formally and explicitly held an extended discussion of the role of replication in the discipline.
However, replication is implicitly at the center of the discipline's nomothetic-ideographic debate \citep{kedron2022replication, sui2021reproducibility} and ongoing discussions about how to construct explanations of the physical and human processes that shape the world \citep[see][]{inkpen2013science, harvey1969, miller2015data, sayer1992method, yeung2019rethinking, yeung2023theory}. 
Within this literature, discussions of replication typically pivot on the expected variability of processes across locations, whether replications can inform theory development and, as a practical matter, the ability to control factors that may affect the outcome of a study.

The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space implying that observable differences between places, and perhaps an inability to replicate prior findings, should be expected across locations. 
Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different location is or is not determined by the same processes.  
In some instances, commentary about differences between locations are extended to point out the uniqueness of places and mixed with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}. 
Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.

Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967} which, applied to locations, alternatively argues that phenomena studied in space cannot be encountered twice, or that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features. 
The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features in different locations, or even to encounter the same arrangement of features at different times in the same location.
In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
In this situation, findings may be expected to replicate and attempting replications can give insight into the stability of processes across locations.

Understanding places as defined by process that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
\cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations. 
In this way, replications can give insight into when, where, and why a explanation does not hold \citep{zhang_wolf_2023}.
Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds. 
In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
In extensive research, replication data is gathered from new context to establish the coverage of an explanation. 
In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.

@@

Geography as a discipline is presently defined by its topical, epistemological, and methodological diversity. 
While replication has been an implicit part of many discussions of the development of knowledge in the discipline, how exactly the practice is understood and applied by researchers within those different traditions remains unclear.
Moreover, to date there has been no empirical measure of how often researchers across the discipline attempt to replicate research, what motivates them to pursue or not pursue replications, and how they would interpret the findings of such studies. 
In fact, we expect that many geographic researcher would disagree with the conception and presentation of replication presented above. 
However, until researcher conceptions and practices of replication are measured conversations about the role of replication in the discipline can only progress so far.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
That OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure \ref{fig:Q7-Epistemology}). 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
In particular, respondents believe that replication studies can be used to assess the construct validity (75\%) and external validity of a prior study.
Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields. 
For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.

@@

While respondents largely agree that replication has some epistemological role to play in the geographic research process, many respondents did not explicitly include these same concepts in their definitions of replicability.
At total of 253 of our respondents provided an interpretable definition of replicability, but only 68 of those definitions (26\%) referenced some form of epistemological function. 
Using replication to externally validate the claims of a study was identified by 49 respondents (19\%).
No other epistemological function was mentioned by more than 13 respondents (5\%).  
In contrast, 123 respondents (48\%) reported that replications could be used to assess or improve how well a prior study conforms to the principles of open science (e.g., sharing procedures).

@@

\noindent More often respondents simply labelled validity checks as the purpose of a replication, as when one researcher defined replicability as, ``The ability to reproduce a study using the same or similar research design to test both its internal and external valdity." 
A number of respondents specializing in qualitative research provided definitions that questioned, or even rejected, the role of replication in their subfield. 
One representative articulates this position by defining replicability as,

\begin{displayquote}
    ``The claim that empirical research of a study can be repeated in the same way as it was done in the study. However, this is not exactly possible in qualitative research, as data collection is always a co-construction between all persons involved in the data collection. Transferred to qualitative research, this means for me rather that one would use the same questions, analyse the data with the same methods, etc. The fact that the results are not necessarily the same is not a weakness, but rather to be expected, since our knowledge is always embedded and co-constructed." 
\end{displayquote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors Affecting the Chances of Replicating a Prior Study}
Overall respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}). 
On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
However, the distribution of these responses is strongly right skewed.
In fact, 47 percent of respondents estimated that less than 10 percent of recent studies have been replicated.
It is similarly unclear if respondents believe recent geographic research could or should be replicated.
On average, respondents estimated that approximately half of studies `could be replicated' (55.0\%) or `should be replicated' (55.9\%). 
However, the distribution of responses to both questions are relatively flat across the range of possible values and highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}), which suggests 
respondents were uncertain whether it was possible or valuable to replicate recent research.  
This pattern of response was consistent across respondents that self-identified as working in different subfields and methodological approaches.

@@

The characteristics of the research team that conducted the original study were generally not identified by respondents as likely to change the changes of replicating that study. 
The majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the unique position of a researcher would decrease, rather than increase, the chances of replicating the claims of a study.
However, only 53 percent of respondents thought the unique position of a researcher would decrease the chances of replicating that study. 
Similarly, 48 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study. 
In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.

Respondents were similarly divided about the extent to which the approach adopted in the prior study would affect the chances of replicating that study. 
Respondents were nearly evenly split as to whether the number of hypotheses tested by a study, and whether that study used qualitative or mixed methods, would increase or decrease an independent researcher's chances of finding results that supported the claims of the prior study.
About a quarter of respondents said that use of a mixed methods approach or the testing of multiple hypotheses had no effect on the chances of replication.
In contrast, a large majority (80\%) of respondents identified the use of quantitative methods in a prior study as increasing the chances of replicating that study. 
This result matches the association observed in respondent definitions of replication, which ties replication to positivist science and quantitative approaches to knowledge creation.

@@

There was less agreement among respondents about whether different characteristics of a phenomenon would impact the chances of replicating the claims made by a prior study of that phenomenon (Figure \ref{fig:Q8-10-Chances}b). 
For all six of the characteristics we examined, at least 12 percent of respondents replied that those factors would have no effect on the chances of replicating a prior study.
Numerous respondents also replied that they simply did not know whether a characteristic would impact the chances of replicating a study. 
For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication. 
Even with this uncertainty, 41 percent of respondents said the presence of spatial dependence was likely to decrease the chances of replicating a prior study.

A majority of respondents did identify the inability to directly measure a phenomenon (61.5\%) and a strong relationship between a phenomenon and local conditions (59.7\%) as reducing the chances of replicating a prior study.
Respondents were roughly evenly divided on whether other factors would increase or decrease the chances of replicating a study.
Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Replications confront existing explanations with new evidence by retesting prior claims using new data and similar research procedures.
Replications can be designed to serve different epistemic functions and to test several forms of validity.
Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories it is based on \citep{earp2015, nichols2021}. 
When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.

@@

The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}. 
Place-to-place variations in phenomena, and the processes that produce those variations, are one of the defining features of geographic research and a central tenet of many of its research traditions.
With these intellectual foundations, it remains unclear how current geographic researchers view replication and its role of in the knowledge accumulation process.
There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availability of research artifacts (e.g., data and code), and address reproducibility rather than replicability. 
In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Replication and the Evaluation of Prior Claims}
Replications structure the iterative development of theory by confronting claims with new evidence.
Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings. 
Until a claim is tested through replication, our expectation of whether it will hold under new conditions relies on the theory used to structure the original investigation, or on a speculative assumption of generalizability.
Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.  
By altering different aspects of a study across a series of replications, researchers can collectively and progressively test claims across a widening set of conditions and use that information to revise theory.

The type of check a replication provides depends on which aspects of a study are changed and in what combination. 
Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}. 
Replication studies are often classified as either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.

Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, then the replication is designed to assess conclusion validity.
As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation. 
Alternatively, if a researcher changes how a key construct is measured and also holds all other aspects of a study constant, then the replication can test construct validity.
Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made. 
Finally, if the materials and procedures (e.g., data collection device, analyses) used in a replication differ from a prior study, then the replication assesses whether these factors affected the original results, thereby testing the internal validity of the prior work.

In conceptual replications, changes are made to the population or location being studied in order to test external validity and whether the claims made in a study generalize to new populations and contexts. 
In geographic research, a conceptual replication could involve changing the location of a study from one city to another, or from one ecosystem to another. 
Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after migration is thought to have changed the population of that area. 
Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
For example, it is not necessarily the case that observing evidence in one location that contradicts a claim made in a prior study of another location would cause a researcher to reduce their confidence in the prior claim.

As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015, haig2022, irvine2021}.
When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
Without these statements, it remains possible that the predictions of the theory will generalize across a large set of contexts. 
In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
In this situation, conceptual replications act as empirical tests of the generalizability of a theory to new contexts. 
Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and /or when the theory is expected to provide meaningful predictions.
As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clear.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{The Replicability of Geographic Research}
Geographers have arguably never formally and explicitly held an extended discussion of the role of replication in the discipline.
However, replication is implicitly at the center of the discipline's nomothetic-ideographic debate \citep{kedron2022replication, sui2021reproducibility} and ongoing discussions about how to construct explanations of the physical and human processes that shape the world \citep[see][]{harvey1969, inkpen2013science, miller2015data, sayer1992method, yeung2019rethinking, yeung2023theory}. 
Within this literature, discussions of replication typically pivot on the expected variability of processes across locations, whether replications can inform theory development and, as a practical matter, the ability to control factors that may affect the outcome of a study.

The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space. 
This principle implies that researchers can expect to observe differences between places, and that perhaps they should expect an inability to replicate prior findings from one place in another.
Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different locations is or is not determined by the same processes.  
In some instances, commentary about differences between places are combined  with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}. 
Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.

Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967}, which, alternatively argues on one hand that phenomena studied in a place cannot be encountered twice, or on the other hand that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features. 
The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features at different times in the same location.
In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
In this situation, findings may be expected to replicate within a range of uncertainty, and attempting replications can give insight into the stability of processes across locations.

Understanding places as defined by processes that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
\cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations. 
In this way, replications can give insight into when, where, and why a explanation does not hold \citep{zhang_wolf_2023}.
Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds. 
In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
In extensive research, replication data is gathered from new context to establish the coverage of an explanation. 
In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.

@@

Geography as a discipline is presently defined by its topical, epistemological, and methodological diversity. 
While replication has been an implicit part of many discussions of the development of knowledge in the discipline, it remains unclear exactly how the practice is understood and applied by researchers within those different traditions.
Moreover, to date there has been no empirical measure of how often researchers across the discipline attempt to replicate research, what motivates them to pursue or not pursue replications, and how they would interpret the findings of such studies. 
In fact, we expect that many geographic researchers would disagree with the conception and presentation of replication presented above. 
However, until researcher conceptions and practices of replication are systematically assessed, conversations about the role of replication in the discipline can only progress so far.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
That OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
Before the start of data collection, we preregistered an analysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions. 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%) (Figure \ref{fig:Q7-Epistemology}).
Respondents also believe that replication studies can be used to investigate and assess whether the variables used in prior studies reflect the concepts that intended to represent (76\%) and whether prior findings resulted from chance variation (66\%).
While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields. 
For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.

@@

While respondents largely agree that replication has some epistemological role to play in the geographic research process, many respondents did not explicitly include these same concepts in their definitions of replicability.
A total of 253 of our respondents provided an interpretable definition of replicability, but only 68 of those definitions (26\%) referenced some form of epistemological function. 
Using replication to externally validate the claims of a study was identified by 49 respondents (19\%).
No other epistemological function was mentioned by more than 13 respondents (5\%).  
In contrast, 123 respondents (48\%) reported that replications could be used to assess or improve how well a prior study conforms to the principles of open science (e.g., sharing data and procedures).

@@

\noindent More often, respondents simply labelled validity checks as the purpose of a replication. One such researcher defined replicability as, ``The ability to reproduce a study using the same or similar research design to test both its internal and external validity."

A number of respondents specializing in qualitative research provided definitions that questioned, or even rejected, the role of replication in their subfield. 
One qualitative researcher articulates this position by defining replicability as,

\begin{displayquote}
    ``the claim that empirical research of a study can be repeated in the same way as it was done in the study. However, this is not exactly possible in qualitative research, as data collection is always a co-construction between all persons involved in the data collection. Transferred to qualitative research, this means for me rather that one would use the same questions, analyse the data with the same methods, etc. The fact that the results are not necessarily the same is not a weakness, but rather to be expected, since our knowledge is always embedded and co-constructed." 
\end{displayquote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors Affecting the Chances of Replicating a Prior Study}
Overall, respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}). 
On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
However, the distribution of these responses is strongly right skewed.
In fact, 47 percent of respondents estimated that less than 10 percent of recent studies have been replicated.
It is similarly unclear if respondents believe recent geographic research could or should be replicated.
On average, respondents estimated that approximately half of studies `could be replicated' (55.0\%) or `should be replicated' (55.9\%). 
However, the distribution of responses to both questions are relatively flat across the range of possible values and highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}), which suggests 
respondents were uncertain whether it was possible or valuable to replicate recent research.  
This pattern of response was consistent across respondents that self-identified as working in different subfields and methodological approaches.

@@

Respondents were generally uncertain or pessimistic about how the characteristics of the researchers and teams of prior studies would change the chances of replicating the studies. 
A majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
More respondents believed that reliance on the unique expertise (48\%) or unique position(s) (53\%) of the researcher(s)  conducting a study would decrease, rather than increase, the chances of replicating the claims of a study.
In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.

Respondents were also divided about the extent to which the approach adopted in the prior study would affect the chances of replicating that study. 
Respondents were nearly evenly split as to whether the number of hypotheses tested by a study, and whether that study used qualitative or mixed methods, would increase or decrease an independent researcher's chances of finding results that supported the claims of the prior study.
About a quarter of respondents said that use of a mixed methods approach or the testing of multiple hypotheses had no effect on the chances of replication.
In contrast, a large majority (80\%) of respondents identified the use of quantitative methods in a prior study as increasing the chances of replicating that study. 
This result matches the association observed in respondent definitions of replication, which ties replication to positivist science and quantitative approaches to knowledge creation.

@@

There was less agreement among respondents about whether different characteristics of a phenomenon would impact the chances of replicating the claims made by a prior study of that phenomenon (Figure \ref{fig:Q8-10-Chances}b). 
For all six of the characteristics we examined, at least 12 percent of respondents replied that those factors would have no effect on the chances of replicating a prior study.
Numerous respondents also replied that they simply did not know whether a characteristic would impact the chances of replicating a study, resulting in a total of 18 to 42 percent of respondents reporting neutral or uncertain opinions about the characteristics of a phenomena and the replicability of research about it.
For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication. 
Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.

Even with this uncertainty, respondents were clearly more concerned about the impact of spatial dependence and place than about spatial heterogeneity.
41 percent of respondents reported that the presence of spatial dependence in a phenomena was likely to decrease the chances of replicating a prior study.
A stronger majority of 59 percent reported that phenomena linked to place-based local conditions would decrease the chances of replication.
Meanwhile, respondents were split about whether spatially variable phenomena would increase or decrease the chances of replication.

Respondents were more decisive about replication issues with inability to measure or manipulate phenomena than about the presence of multiple possible explanations.
A majority of respondents identified the inability to directly measure a phenomenon (61.5\%) as reducing the chances of replicating a prior study.
A large number of respondents (42\%) were either neutral or undecided on whether the inability to experimentally manipulate a phenomena impacts the replicability of studies about it, with a majority of the remaining respondents agreeing that this inability would decrease the chances of replication. 
An equally large number of respondents were neutral or undecided on whether the presence of a large number of plausible explanations for a phenomena would impact the chances of replicating studies about it, with no clear trend.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Factors that Affect the Decision to Attempt Replications}
Several factors related to academic incentives and the availability of prior study research artifacts appear to affect whether researchers decide to attempt to replicate recent geographic research, with relative less concern about the characteristics of prior studies (Figure \ref{fig:Q15-DecisionFactors}).
